\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-30 paper.tex
expanding sections

The video game industry has readily embraced augmented reality, leading to the
development of many AR games for smartphones and dedicated head-mounted
displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
downloaded over a billion times~\autocite{webster2018}. This game makes use of
GPS and camera data to overlay game objects (in this case fictional monsters) on
top of images of the real world~\autocite{concepcion2016} (see Figure
\ref{fig:pokemonGo}).

@@

%TODO write this section
TODO: write this section

@@

The design of the Editour is agnostic about how the media will be used. For an
app like izi.TRAVEL, the images are displayed when the associated audio tour is
playing. The tour files produced by Editour could theoretically be used by a
tour guide app that does not incorporate AR.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met
up with Atticus, the IQP group, and our friend Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how
the app works we had each of them try going through Kinkaku-ji while
listening to the tour and using the app's features. Each member of our team
also installed the beta version so we could test it.

@@

We also noticed that we were only able to augment a maximum of two image targets
at a time. In almost all cases, only two translatable signs were in view at
once. The only scenario in which there were more than two image targets in view
at a given time was with the four framed photos of the interior, which were
arranged in a two by two grid. When standing at a distance from the grid, only
two images would be augmented with the blue information button. By default,
Vuforia limits the amount of image targets that the engine should accept
simultaneously. In the Vuforia engine settings, we changed this limit to
accommodate for four simultaneous images

@@

	Agree & Agree & Strongly agree & Neutral & Agree & Increasing GPS accuracy
	of course. Adding a tracking "you are here" marker to the route. \\

>>>>

The video game industry has readily embraced augmented reality, leading to the
development of many AR games for smartphones and dedicated head-mounted
displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
downloaded over a billion times~\autocite{webster2018}. This game makes use of
GPS and camera data to overlay game objects (in this case fictional monsters) on
top of images of the real world~\autocite{concepcion2016} (see
Figure~\ref{fig:pokemonGo}).

@@

Unity is a game engine that was originally introduced in
2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
and price-wise---the engine quickly became incredibly popular. Ironically,
because the engine is so accessible that, Unity has faced a degree of critism.
Because Unity appeals to so many beginners, there are many unpolished games that
bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
global communications at Unity, "Democratizing development---in our minds, we
don’t think is the wrong thing, we think it’s the right thing. You want more
people understanding, and everyone’s gotta start somewhere." Unity CEO John
Riccitiello made the claim at TechCrunch Disrupt San Francisco that half of all
games are made with Unity \autocite{dillet2018}. We consider Unity's ubiquity to
be an advantage; there is a glut of information about how to use augmented
reality within Unity.
%TODO citing a quotation from inside the first citation. Is this okay?

Even though Unity is beginner-friendly for making games, the augmented reality
app we planned to create was not a game. Therefore, we were somewhat concerned
that Unity's ease-of-use would be undermined simply because we were not making a
traditional game experience. Instead we would be using Unity to create a piece
of software that both looked and felt like a familiar mobile app. Unity has very
limited support for this compared to technologies that are specifically geared
toward creating modern mobile user interfaces such as React.

At the same time, Unity has excellent support for augmented reality through
various extensions. Because we initially understood AR to be the core of the app
experience, we chose to use Unity with the Vuforia extension for all future
development on the mobile app.

Unity is distinct from the technologies previously discussed in this section
because it is not an AR platform unto itself. Instead, Unity can take advantage
of AR platforms such as ARKit, ARCore, Vuforia and Wikitude through the use of
plugins.
%TODO provide citations that note that all of these platforms support Unity.

@@

Furthermore, we foresee Editour being a useful tool outside of the app we
designed for Kyoto VR. The design of the Editour is agnostic about how the media
will be used. For an app like izi.TRAVEL, the images are displayed when the
associated audio tour is playing.

The files produced by Editour could be used to power an app that does not
incorporate AR, such as an audio guide mobile web app that runs entirely in the
browser, using the geolocation API to access the user's location (if the user
grants permission.) This kind of infrastructure would allow users to access an
audio tour---supplemented by images and audio transcripts---without the need to
download an app at all. By simply visiting a link, a user could experience a
guided tour that changes as the user walks through the route. For example,
colleges could distribute tour links via QR codes, which would instantly launch
an interactive guided tour of the campus through the browser.

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under an
open-source license. This allows anyone to expand the frontend and backend to
suit their needs. With additional hardware and by extending the current
implementation of both the frontend and backend, Editour could be used as the
groundwork to create an entire crowd-sourced walking tour platform, allowing
users to design tours for others to take.

In summary, we want to explore the idea of creating a community-driven audio
tour database that allows mobile users to take tours without the need to install
an app. The open-source code we wrote for Editour empowers us (or anyone else)
to develop and launch this platform in the future.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of ARuko in order to conduct some final testing. We met up with
Atticus, the IQP group, and our friend Hikaru and installed the beta version of
ARuko on each of their phones. With little instruction about how the app works
we had each of them try going through Kinkaku-ji while listening to the tour and
using the app's features. Each member of our team also installed the beta
version so we could test it.

@@

We also noticed that we were only able to augment a maximum of two image targets
at a time. In almost all cases, only two translatable signs were in view at
once. The only scenario in which there were more than two image targets in view
at a given time was with the four framed photos of the interior, which were
arranged in a two by two grid. When standing at a distance from the grid, only
two images would be augmented with the blue information button. By default,
Vuforia limits the amount of image targets that the engine should accept
simultaneously. In the Vuforia engine settings, we changed this limit to
accommodate for four simultaneous images.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
	\caption{The result of increasing the size of the info buttons and increasing
    the maximum image target count to four}
	\label{fig:fourIButtons}
\end{figure}

@@

	Agree & Agree & Strongly agree & Neutral & Agree & Increasing GPS accuracy
	of course. Adding a tracking ``you are here'' marker to the route. \\
